Predicting US Presidential Elections

### 2024-11-02 paper/paper.qmd

---
title: "Where are Torontonians likely to get married"
subtitle: "Analysing the different marriage offices around GTA"
author: 
  - Aamishi Avarsekar
thanks: "Code and data are available at: https://github.com/aamishi/marriages_weekly_reflection/tree/master"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Predicting US Presidential Elections"
subtitle: "Analysing Electoral Polls to Model Forecast the Winner of the Upcoming US Presidential Election"
author: 
  - Aamishi Avarsekar
  - Gauravpreet Thind
  - Divya Gupta
thanks: "Code and data are available at: https://github.com/aamishi/marriages_weekly_reflection/tree/master"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
